---
title: "Database Status"
author: "Brent Morrison"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output:
  html_document:
    fig_caption: yes
    theme: spacelab #sandstone #spacelab #flatly
    highlight: pygments
    toc: TRUE
    toc_depth: 3
    number_sections: TRUE
    toc_float:
      smooth_scroll: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
```

# Database status

This document exposes a status report for the "Stock_Master" database.  This is intended to show the update status of raw data ingested to the database, transformation performed and results written.  

```{r}
# Imports
library(jsonlite)
library(DT)
library(kableExtra)
library(ggplot2)
library(lubridate)
library(dplyr)
library(tidyr)
library(DBI)
library(RPostgres)
```


```{r}
# Database connection
config <- read_json('config.json')

con <- dbConnect(
  RPostgres::Postgres(),
  host      = 'localhost',
  port      = '5432',
  dbname    = 'stock_master',
  user      = 'postgres',
  password  = config$pg_password
)
```


## Fundamental data  

### SEC Edgar data 

Raw data from the DERA website.

```{r}
sql1 <- "select 'sub' as table, sec_qtr, count(*) as n from edgar.sub group by 1,2 order by 2 desc, 1 asc"
qry1 <- dbSendQuery(conn = con, statement = sql1) 
fund_raw_data <- dbFetch(qry1)

qtr_to_date <- function(x){
  as.Date(ISOdate(
    ifelse(substr(x,6,6) == '4', as.numeric(substr(x,1,4))+1, substr(x,1,4)),
    ifelse(substr(x,6,6) == '4', 1, as.numeric(substr(x,6,6))*3+1),
    1
  ))-1
}

fund_raw_data$date_stamp <- qtr_to_date(fund_raw_data$sec_qtr)
```

<br>

```{r}
date_filter <- as.Date(ISOdate(as.numeric(format(max(fund_raw_data$date_stamp), "%Y"))-1,1,1))

kbl(fund_raw_data[fund_raw_data$date_stamp > date_filter, ]) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

<br>

```{r}
DT::datatable(
  fund_raw_data,
  rownames= FALSE, 
  height = 200,
    options = list(
    #pageLength = 6,
    dom = 't <"bottom" p>',
    #dom = 'pt', 
    columnDefs = list(list(className = 'dt-center', targets = 0:1))
    )
)
```


### SEC Edgar data (processed)

Status of data inserted into ```edgar.edgar_fndmntl_all_tb```

```{r}
sql2 <- "select sec_qtr, count(*) as n from edgar.edgar_fndmntl_all_tb group by 1 order by 1 desc"
qry2 <- dbSendQuery(conn = con, statement = sql2) 
fund_data <- dbFetch(qry2)

DT::datatable(
  fund_data,
  rownames= FALSE,
  height = 200,
  options = list(
    #pageLength = 6,
    dom = 't <"bottom" p>',
    columnDefs = list(list(className = 'dt-center', targets = 0))
    ) #scrollX = TRUE, 
)
```

<br>

```{r}
dbDisconnect(con)
```


For examples on using R Markdown see <https://github.com/betanalpha/knitr_case_studies/blob/master/generative_modeling/generative_modeling.Rmd> and <https://betanalpha.github.io/assets/case_studies/generative_modeling.html>.

[DT column alignment](https://stackoverflow.com/questions/35749389/column-alignment-in-dt-datatable)
